---
title: "`r response` (rhythm-`r rhythm`)"
author: "Tomas Lenc"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document: 
    code_folding: show
    toc: true
    toc_float: 
      collapsed: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

source('config.R')
source('lib/utils.R')
source('lib/figures.R')

```


# Parameters 

```{r}
task <- 'listen'

# responsiveness z-score threshold 
z_snr_thr = ifelse(str_detect(response, 'biLFP'), qnorm(1-0.05), qnorm(1-0.01))

# plotting y axis limits 
if (rhythm=='sp') {
    ylims_fft <- c(-1.1, 1.2)# c(-0.8, 1.5) 
    ylims_acf <- c(-1.1, 1.2)
} else if (rhythm=='wp') {
    ylims_fft <- c(-0.7, 0.7) # c(-0.7, 1.2)
    ylims_acf <- c(-1, 1)
}

# file names and paths 
save_prefix <- sprintf('response-%s_rhythm-%s_task-%s', response, rhythm, task)
anat_prefix <- ifelse(str_detect(response, 'bi'), 'bipolar_elecs_all', 'TDT_elecs_all')
    
```

<br> 

# Stimulus and brainstem model 

Stimulus envelope.  
```{r}
# load stimulus envelope  
df_hilbert_fft <- read.csv(file.path(feat_path, 'response-hilbert_fftAggrFreq.csv'))
df_hilbert_fft <- fixFactors(df_hilbert_fft)

df_hilbert_acf <- read.csv(file.path(feat_path, 'response-hilbert_aggrACFtrial.csv'))
df_hilbert_acf <- fixFactors(df_hilbert_acf)
df_hilbert_acf <- select(df_hilbert_acf, rhythm, z_meterRel)

sprintf('Stimulus envelope FFT-based beat index = %.2f', 
        filter(df_hilbert_fft, rhythm==!!rhythm) %>% pull(z_meterRel))

sprintf('Stimulus envelope ACF-based beat index = %.2f', 
        filter(df_hilbert_acf, rhythm==!!rhythm) %>% pull(z_meterRel))
```

<br> 

Spectral flux.  

```{r}
df_flux_fft <- read.csv(file.path(feat_path, 'response-flux_fftAggrFreq.csv'))
df_flux_fft <- fixFactors(df_flux_fft)

df_flux_acf <- read.csv(file.path(feat_path, 'response-flux_aggrACFtrial.csv'))
df_flux_acf <- fixFactors(df_flux_acf)
df_flux_acf <- select(df_flux_acf, rhythm, z_meterRel)

sprintf('Spectral flux FFT-based beat index = %.2f', 
        filter(df_flux_fft, rhythm==!!rhythm) %>% pull(z_meterRel))

sprintf('Spectral flux ACF-based beat index = %.2f', 
        filter(df_flux_acf, rhythm==!!rhythm) %>% pull(z_meterRel))
```

<br> 

Brainstem model.  
```{r}
if (auditory_model_type == 'an'){
    
    df_urear_fft <- read.csv(file.path(feat_path, 'response-an_fftAggrFreq.csv'))
    df_urear_fft <- fixFactors(df_urear_fft)
    
    df_urear_acf <- read.csv(file.path(feat_path, 'response-an_aggrACFtrial.csv'))
    df_urear_acf <- fixFactors(df_urear_acf)

} else if (auditory_model_type == 'ic'){
    
    df_urear_fft <- read.csv(file.path(feat_path, 'response-ic_fftAggrFreq.csv'))
    df_urear_fft <- fixFactors(df_urear_fft)
    
    df_urear_acf <- read.csv(file.path(feat_path, 'response-ic_aggrACFtrial.csv'))
    df_urear_acf <- fixFactors(df_urear_acf)

}

df_urear_acf <- select(df_urear_acf, rhythm, z_meterRel)

sprintf('Brainstem model FFT-based beat index = %.2f', 
        filter(df_urear_fft, rhythm==!!rhythm) %>% pull(z_meterRel))

sprintf('Brainstem model ACF-based beat index = %.2f', 
        filter(df_urear_acf, rhythm==!!rhythm) %>% pull(z_meterRel))

```




<br> 

# Contact responsiveness

```{r}

# =======================
# contact responsiveness
# =======================

# prepare dataframe with a list of responsive contacts 
df_resp <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_fftAggrFreq.csv', response)))
df_resp <- fixFactors(df_resp)

# subset only listening wp 
df_resp <- filter(df_resp, task=='listen' & rhythm=='wp')

# get info about responsive contacts 
df_resp$responsive <- df_resp$z_snr > z_snr_thr
df_resp <- select(df_resp, subject, elec, responsive)
    
# prepare dataframe with z-snr 
df_zsnr_all <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_fftAggrFreq.csv', response)))
df_zsnr_all <- fixFactors(df_zsnr_all)

df_zsnr_all <- dplyr::inner_join(df_zsnr_all, df_resp)
df_zsnr_all <- df_zsnr_all %>% select(subject, elec, rhythm, task, z_snr, responsive)

# subset responsive 
df_zsnr_responsive <- df_zsnr_all %>% filter(responsive == TRUE)

# load responses to distortion products above 130 Hz 
df_crossmod <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_ffrAggrCrossmod.csv', response)))
df_crossmod <- fixFactors(df_crossmod)

# subset responsive 
df_crossmod_responsive <- df_crossmod %>% 
    filter(task=='listen' & rhythm=='wp' & z_snr > z_snr_thr) %>% 
    select(subject, elec, z_snr)

```


<br> 

# Global contact counts 

```{r}

# load anatomy
df_anat <- read.csv(file.path(feat_path, sprintf('prefix-%s_anatomy.csv', anat_prefix)))
df_anat <- fixFactors(df_anat)

# N participants
N_sub <- length(unique(df_anat$subject))

# total N electrodes 
N_elec <- nrow(df_anat)

# N in gray matter
N_elec_in_gray <- df_anat %>% filter(in_gray==1) %>% nrow()

# N in gray matter per hemisphere
N_elec_in_gray_per_hem <- df_anat %>% filter(in_gray==1) %>% count(hem)

# total N responsive 
N_elec_resp <- sum(df_zsnr_all$responsive)

# N across all auditory ROIs
N_elec_auditory <- df_anat %>% filter(custom %in% auditory_rois & custom != 'unknown') %>% nrow
N_elec_auditory_per_sub <- df_anat %>% filter(custom %in% auditory_rois & custom != 'unknown') %>% count(subject)

# N across all higher-level ROIs
N_elec_assoc <- df_anat %>% filter(custom %in% assoc_rois & custom != 'unknown') %>% nrow
N_elec_assoc_per_sub <- df_anat %>% filter(custom %in% assoc_rois & custom != 'unknown') %>% count(subject)

# N contacts across all ROIs
N_elec_rois <- df_anat %>% filter(custom != 'unknown') %>% nrow
N_elec_rois_lh <- df_anat %>% filter(custom != 'unknown' & hem == 'lh') %>% nrow
N_elec_rois_rh <- df_anat %>% filter(custom != 'unknown' & hem == 'rh') %>% nrow
N_sub_rois <- df_anat %>% filter(custom != 'unknown') %>% count(subject)

# how many electrode arrays were implanted in total 
df <- filter(df_anat, custom != 'unknown')
df$shaft <- str_extract(df$elec, '^[^0-9]+')
df$sub_shaft <- str_c(df$subject, df$shaft, sep="_")
N_shafts_rois <- length(unique(df$sub_shaft))

sprintf('%d subjects', N_sub)
sprintf('%d electrode arrays', N_shafts_rois)
sprintf('%d contacts total', N_elec_rois)
sprintf('%d contacts in LH', N_elec_rois_lh)
sprintf('%d contacts in RH', N_elec_rois_rh)

```



<br> 

# Primary auditory cortex (anatomically defined)

Prepare contacts.  

```{r}

# load anatomy
df_anat <- read.csv(file.path(feat_path, sprintf('prefix-%s_anatomy.csv', anat_prefix)))
df_anat <- fixFactors(df_anat)

# get only contacts in HG
df_anat <- filter(df_anat, custom %in% c('HG'))

```


<br>   

## FFT 

```{r}
# load FFT 
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_fftAggrFreq.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task & rhythm==!!rhythm)

# subset + add anatomy  
df_data <- dplyr::inner_join(df_data, df_anat)
sprintf('N contacts total = %d', nrow(df_data))

# add responsiveness info 
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive))

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)
sprintf('N contacts responsive = %d', nrow(df_data))

```

```{r}

df_summary <- summarySE(df_data, measurevar='z_snr', groupvars=c('custom'))
sprintf('mean zSNR in HG: %.2f, 95%% CI [%.2f, %.2f]',
        df_summary$z_snr, 
        df_summary$z_snr-df_summary$ci, 
        df_summary$z_snr+df_summary$ci)

```

```{r}

df_summary <- summarySE(df_data, measurevar='z_meterRel', groupvars=c('custom'))
sprintf('mean beat index in HG: %.2f, 95%% CI [%.2f, %.2f]',
        df_summary$z_meterRel, 
        df_summary$z_meterRel-df_summary$ci, 
        df_summary$z_meterRel+df_summary$ci)


```

<br>    

Compare beat-index against the brainstem model (one-sample t-test).  

```{r}
mu <- filter(df_urear_fft, rhythm==!!rhythm) %>% pull(z_meterRel)
t.test(df_data$z_meterRel, mu=mu)
```

<br>   

Compare beat-index against zero (one-sample t-test).  

```{r}
t.test(df_data$z_meterRel, mu=0)
```

<br>   

Plot the data.  

```{r, fig.height=4, fig.width=5}
plt <- plot_feature(df_data, feature_name='z_meterRel', atlas='custom', task='listen', hline_spec=mu,
                    pntsize_ind='z_snr', pnt_col='lut', pnt_col_mean='black', hline_col='grey70',
                    y_lims=ylims_fft, hline_zero=show_zero_line) 
plt
```



<br>   

## ACF 

```{r}

# load ACF trial 
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_aggrACFtrial.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task & rhythm==!!rhythm)

# subset + add anatomy  
df_data <- dplyr::inner_join(df_data, df_anat)
nrow(df_data)

# add responsiveness info 
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive, z_snr))

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)
nrow(df_data)


```

<br>    

Compare beat-index against the brainstem model (one-sample t-test).  

```{r} 
mu <- filter(df_urear_acf, rhythm==!!rhythm) %>% pull(z_meterRel)

t.test(df_data$z_meterRel, mu=mu)


```

<br>    

Compare beat-index against zero (one-sample t-test).  

```{r}
t.test(df_data$z_meterRel, mu=0)


```

<br>    

Plot the data.    

```{r, fig.height=4, fig.width=5}
plt <- plot_feature(df_data, feature_name='z_meterRel', atlas='custom', task='listen', hline_spec=mu,
                    pntsize_ind='z_snr', pnt_col='lut', pnt_col_mean='black', hline_col='grey70',
                    y_lims=ylims_acf, hline_zero=show_zero_line) 
plt

```




<br> 

# PAC (anatomically+functionally defined)


<br>   

Prepare contacts.  

```{r}
# load anatomy
df_anat <- read.csv(file.path(feat_path, sprintf('prefix-%s_anatomy.csv', anat_prefix)))
df_anat <- fixFactors(df_anat)

# get only contacts in HG
df_anat <- filter(df_anat, custom %in% c('HG'))
```


<br>   

## FFT 

```{r}
# load FFT 
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_fftAggrFreq.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task & rhythm==!!rhythm)

# subset + add anatomy  
df_data <- dplyr::inner_join(df_data, df_anat)
sprintf('N contacts total = %d', nrow(df_data))

# add responsiveness info 
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive))

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)
sprintf('N contacts responsive = %d', nrow(df_data))

# subset responsive to crossmod above 130 Hz 
df_data <- dplyr::inner_join(df_data, select(df_crossmod_responsive, subject, elec))
sprintf('N contacts responsive & above 130 Hz = %d', nrow(df_data))

# save the data frame for plotting in python 
write.csv(df_data, 
          file.path(save_path, sprintf('%s_atlas-functionalPAC_fft.csv', save_prefix)), 
          row.names=F)

# let's keep this for later (to show PAC elecs in plots)
df_pac <- df_data %>% select(subject, elec)

```

<br>    

Compare beat-index against the brainstem model (one-sample t-test).  

```{r} 
mu <- filter(df_urear_fft, rhythm==!!rhythm) %>% pull(z_meterRel)
t.test(df_data$z_meterRel, mu=mu)
```
<br>    

Compare beat-index against zero (one-sample t-test).  

```{r} 
t.test(df_data$z_meterRel, mu=0)
```

<br>    

Plot the data.  

```{r, fig.height=4, fig.width=5}
plt <- plot_feature(df_data, feature_name='z_meterRel', atlas='custom', task='listen', hline_spec=mu,
                    pntsize_ind='z_snr', pnt_col='lut', pnt_col_mean='black', hline_col='grey70',
                    y_lims=ylims_fft, hline_zero=show_zero_line) 

plt
```



<br>   

## ACF 

```{r}
# load ACF 
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_aggrACFtrial.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task & rhythm==!!rhythm)

# subset + add anatomy  
df_data <- dplyr::inner_join(df_data, df_anat)
sprintf('N contacts total = %d', nrow(df_data))

# add responsiveness info 
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive, z_snr))

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)
sprintf('N contacts responsive = %d', nrow(df_data))

# subset responsive to crossmod above 100 Hz 
df_data <- dplyr::inner_join(df_data, select(df_crossmod_responsive, subject, elec))
sprintf('N contacts responsive & above 130 Hz = %d', nrow(df_data))

```

<br>    

Compare beat-index against the brainstem model (one-sample t-test).  

```{r} 
mu <- filter(df_urear_acf, rhythm==!!rhythm) %>% pull(z_meterRel)
t.test(df_data$z_meterRel, mu=mu)
```

<br>    

Compare beat-index against zero (one-sample t-test).  

```{r} 
t.test(df_data$z_meterRel, mu=0)
```

<br>    

Plot the data.  

```{r, fig.height=4, fig.width=5}
# plt <- plot_feature(df_data, feature_name='z_meterRel', atlas='custom', task='listen', hline_spec=mu,
#                     pntsize_ind=1.2, pnt_col='lut', pnt_col_mean='black', hline_col='grey70',
#                     y_lims=ylims_acf, hline_zero=show_zero_line) 
plt <- plot_feature(df_data, feature_name='z_meterRel', atlas='custom', task='listen', hline_spec=mu,
                    pntsize_ind='z_snr', pnt_col='lut', pnt_col_mean='black', hline_col='grey70',
                    y_lims=ylims_fft, hline_zero=show_zero_line) 

plt
```






<br> 

# Auditory ROIs



<br>   

Prepare contacts.  

```{r}
atlas_name <- 'auditory'

# load anatomy
df_anat <- read.csv(file.path(feat_path, sprintf('prefix-%s_anatomy.csv', anat_prefix)))
df_anat <- fixFactors(df_anat)

# select only in custom atlas 
df_anat <- filter(df_anat, custom %in% auditory_rois)

# set ROI order for plotting
df_anat$custom <- factor(df_anat$custom, levels=auditory_rois)

df_count_all <- count_elec_roi(df_anat, 'custom')

# subset responsive 
df_anat_resp <- dplyr::inner_join(df_anat, 
                                  df_zsnr_responsive %>% 
                                      filter(rhythm==!!rhythm & task==!!task) %>%
                                      select(subject, elec))

df_count_resp <- count_elec_roi(df_anat_resp, 'custom')
```

```{r}
# show the output 
pander(merge(df_count_all, df_count_resp, by='custom', suffixes=c('_total', '_responsive')) %>% rename(roi=custom))
```

```{r}

plt <- plot_count_roi_resp(df_count_all, df_count_resp, 'custom')

save_fig(file.path(save_path_fig, sprintf('%s_atlas-%s_responsive_counts', save_prefix, atlas_name)), 
         plt, width=5, height=4, png=F)

plt

```



<br>   

## FFT

```{r}

# load FFT
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_fftAggrFreq.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task & rhythm==!!rhythm)

# subset + add anatomy  
df_data <- dplyr::inner_join(df_data, df_anat)

# add responsiveness info 
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive))

# add info about PAC 
df_data$pac <- str_c(df_data$subject, df_data$elec) %in% str_c(df_pac$subject, df_pac$elec)
stopifnot(length(df_data$pac) != nrow(df_pac))

# save
write.csv(df_data, 
          file.path(save_path, sprintf('%s_atlas-%s_fft.csv', save_prefix, atlas_name)), 
          row.names=F)

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)

# rename atlas column name to "roi"
df_data <- rename(df_data, roi=custom)

```

<br>    

```{r} 
mu <- filter(df_urear_fft, rhythm==!!rhythm) %>% pull(z_meterRel)

plt <- plot_feature(df_data, feature_name='z_meterRel', atlas='roi', task='listen', 
                    edgehighligh_name='pac', hline_spec=mu, hline_col='grey70', 
                    pntsize_ind=2, pntalpha_ind=0.5, pnt_col='lut', dodge_width=0.2,
                    pnt_col_mean='black', pntsize_mean=3, size_err=1.1, width_err=0,
                    y_lims=ylims_fft, show_labels=F, hline_zero=show_zero_line)
plt

save_fig(file.path(save_path_fig, sprintf('%s_atlas-%s_urear-%s_zbeatFFT',
                                          save_prefix, atlas_name, auditory_model_type)), 
         plt, width=1.9, height=2.5, png=F)

```

<br>    

Compare across ROIs.  

```{r} 
# mixed model 
m <- lmer(z_meterRel ~ roi + (1|subject), data=df_data)
prep_anova_for_print(Anova(m, test='F'))
```

```{r} 
prep_bf_for_print(anovaBF(z_meterRel ~ roi + subject, data=df_data, whichRandom='subject', progress=F))
```

<br>    

Posthoc tests.  

```{r} 
pander(pairwise_contrasts_one_cond(m, var='roi', adjust_method='fdr', return_ci=TRUE)$res)
```

<br>    

Compare beat-index against the brainstem model (one-sample t-test).  

```{r} 
df_against_mu <- ddply(df_data, c('roi'), ttest_against_mu, mu=mu)
df_against_mu$pval <- p.adjust(df_against_mu$pval, method='fdr')
df_against_mu$signif <- signifStars(df_against_mu$pval)
pander(df_against_mu)

```

<br>    

Compare beat-index against zero (one-sample t-test).  

```{r} 
df_against_0 <- ddply(df_data, c('roi'), ttest_against_mu, mu=0)
df_against_0$pval <- p.adjust(df_against_0$pval, method='fdr')
df_against_0$signif <- signifStars(df_against_0$pval)
pander(df_against_0)

```



<br>   

## ACF 

```{r}
# load ACF
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_aggrACFtrial.csv', response)))
df_data <- fixFactors(df_data)

# subset in custom atlas 
df_data <- dplyr::inner_join(df_data, df_anat)

# subset rhythm and task
df_data <- filter(df_data, task==!!task & rhythm==!!rhythm)

# add info about responsiveness
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive))

# add info about PAC 
df_data$pac <- str_c(df_data$subject, df_data$elec) %in% str_c(df_pac$subject, df_pac$elec)
stopifnot(length(df_data$pac) != nrow(df_pac))

# save
write.csv(df_data, 
          file.path(save_path, sprintf('%s_atlas-%s_acfTrial.csv', save_prefix, atlas_name)), 
          row.names=F)

# subset responsive 
df_data <- df_data %>% filter(responsive == TRUE)

# rename atlas column name to "roi"
df_data <- rename(df_data, roi=custom)

```

<br>    

```{r} 

mu <- filter(df_urear_acf, rhythm==!!rhythm) %>% pull(z_meterRel)

plt <- plot_feature(df_data, feature_name='z_meterRel', atlas='roi', task='listen', hline_spec=mu, hline_col='grey70', 
                    edgehighligh_name='pac', pntsize_ind=2, pntalpha_ind=0.5, pnt_col='lut', dodge_width=0.2,
                    pnt_col_mean='black', pntsize_mean=3, size_err=1.1, width_err=0,
                    y_lims=ylims_acf, show_labels=F, hline_zero=show_zero_line) 
plt

save_fig(file.path(save_path_fig, sprintf('%s_atlas-%s_urear-%s_zbeatACFtrial', 
                                          save_prefix, atlas_name, auditory_model_type)), 
         plt, width=1.9, height=2.5, png=F)


```

<br>    
 
Compare across regions.  

```{r} 
m <- lmer(z_meterRel ~ roi + (1|subject), data=df_data)
prep_anova_for_print(Anova(m, test='F'))
```

<br>    


```{r} 
prep_bf_for_print(anovaBF(z_meterRel ~ roi + subject, data=df_data, whichRandom='subject', progress=F))
```

<br>    

Posthoc tests.  

```{r} 
pander(pairwise_contrasts_one_cond(m, var='roi', adjust_method='fdr', return_ci=TRUE)$res)
```

<br>    

Compare beat-index against the brainstem model (one-sample t-test).  

```{r} 
df_against_mu <- ddply(df_data, c('roi'), ttest_against_mu, mu=mu)
df_against_mu$pval <- p.adjust(df_against_mu$pval, method='fdr')
df_against_mu$signif <- signifStars(df_against_mu$pval)
pander(df_against_mu)
```

<br>    

Compare beat-index against zero (one-sample t-test).  

```{r} 
df_against_0 <- ddply(df_data, c('roi'), ttest_against_mu, mu=0)
df_against_0$pval <- p.adjust(df_against_0$pval, method='fdr')
df_against_0$signif <- signifStars(df_against_0$pval)
pander(df_against_0)
```





<br> 

# Associative ROIs


<br>

Prepare contacts.  

```{r}
atlas_name <- 'assoc'

# load anatomy
df_anat <- read.csv(file.path(feat_path, sprintf('prefix-%s_anatomy.csv', anat_prefix)))
df_anat <- fixFactors(df_anat)

df_anat <- dplyr::filter(df_anat, custom %in% c('HG', assoc_rois))
df_anat$custom <- droplevels(df_anat$custom)
df_anat$custom <- factor(df_anat$custom, levels=c('HG', assoc_rois))

# subset responsive 
df_anat_resp <- dplyr::inner_join(df_anat, 
                                  df_zsnr_responsive %>% 
                                      filter(rhythm==!!rhythm & task==!!task) %>%
                                      select(subject, elec))

# check counts
df_count_all <- count_elec_roi(df_anat, 'custom')
df_count_resp <- count_elec_roi(df_anat_resp, 'custom')
pander(merge(df_count_all, df_count_resp, by='custom', suffixes=c('_total', '_responsive')) %>% rename(roi=custom))
```

Remove ROIs without enough responsive contacts.  

```{r}
## !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
if (response == 'LFP'){
    # remove SFG (too little responsive electrodes)
    bad_rois <- c('SFG')
} else if (response == 'biLFP'){
    # remove SFG and MFG (too little responsive electrodes)
    bad_rois <- c('SFG', 'MFG')
}
df_anat <- filter(df_anat, !custom %in% bad_rois) %>% droplevels()
df_anat_resp <- filter(df_anat_resp, !custom %in% bad_rois) %>% droplevels()
## !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

# recount
df_count_all <- count_elec_roi(df_anat, 'custom')
df_count_resp <- count_elec_roi(df_anat_resp, 'custom')
pander(merge(df_count_all, df_count_resp, by='custom', suffixes=c('_total', '_responsive')) %>% rename(roi=custom))

```

```{r}

plt <- plot_count_roi_resp(df_count_all, df_count_resp, 'custom')
plt 

save_fig(file.path(save_path_fig, sprintf('%s_atlas-%s_responsive_counts', save_prefix, atlas_name)),
         plt, width=5, height=4, png=F)


```



<br>   

## FFT 

```{r}
# load FFT
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_fftAggrFreq.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task & rhythm==!!rhythm)

# subset in ROIs
df_data <- dplyr::inner_join(df_data, df_anat)

# add info about responsiveness
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive))

# save
write.csv(df_data, 
          file.path(save_path, sprintf('%s_atlas-%s_fft.csv', save_prefix, atlas_name)), 
          row.names=F)

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)

# rename atlas column name to "roi"
df_data <- rename(df_data, roi=custom)
```

<br>    

```{r} 

mu <- filter(df_urear_fft, rhythm==!!rhythm) %>% pull(z_meterRel)

plt <- plot_feature(df_data, feature_name='z_meterRel', atlas='roi', task='listen', 
                    hline_spec=mu, hline_col='grey70', 
                    pntsize_ind=2, pntalpha_ind=0.5, pnt_col='lut', dodge_width=0.2,
                    pnt_col_mean='black', pntsize_mean=3, size_err=1.1, width_err=0,
                    y_lims=ylims_fft, show_labels=F, hline_zero=show_zero_line) 
plt
 
save_fig(file.path(save_path_fig, sprintf('%s_atlas-%s_urear-%s_zbeatFFT', 
                                          save_prefix, auditory_model_type, atlas_name)), 
         plt, width=1.9, height=2.5, png=F)

```

<br>    

### Model beat index

```{r} 
# mixed model 
m <- lmer(z_meterRel ~ roi + (1|subject), data=df_data)
prep_anova_for_print(Anova(m, test='F'))
```

<br>    

```{r} 
prep_bf_for_print(anovaBF(z_meterRel ~ roi + subject, data=df_data, whichRandom='subject', progress=F))
```

<br>    

```{r} 
# posthoc 
pander(pairwise_contrasts_one_cond(m, var='roi', adjust_method='fdr', return_ci=TRUE)$res)
```

<br>    

Compare beat-index against the brainstem model (one-sample t-test).  

```{r} 
df_against_mu <- ddply(df_data, c('roi'), ttest_against_mu, mu=mu)
df_against_mu$pval <- p.adjust(df_against_mu$pval, method='fdr')
df_against_mu$signif <- signifStars(df_against_mu$pval)
pander(df_against_mu)
```

<br>    

Compare beat-index against zero (one-sample t-test).  

```{r} 
df_against_0 <- ddply(df_data, c('roi'), ttest_against_mu, mu=0)
df_against_0$pval <- p.adjust(df_against_0$pval, method='fdr')
df_against_0$signif <- signifStars(df_against_0$pval)
pander(df_against_0)
```


<br>  

### Model SNR

Model with z-snr directly as dependent variable.   

```{r}
# we'll do the same as when comparing beat index across associative ROIs
df_data$z_snr_log <- log_trans(df_data$z_snr)

# only for sp rhythm? (see Results section for context)
m_zsnr <- lmer(z_snr_log ~ roi + (1|subject), data=df_data)

prep_anova_for_print(Anova(m_zsnr, test='F'))
```

```{r}
prep_bf_for_print(anovaBF(z_snr_log ~ roi + subject, data=df_data, whichRandom='subject', progress=F))
```

```{r}
pander(pairwise_contrasts_one_cond(m_zsnr, var='roi', adjust_method='fdr', return_ci=TRUE)$res)
```






<br>   

## ACF 

```{r}
# load ACF
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_aggrACFtrial.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task & rhythm==!!rhythm)

# subset in ROIs
df_data <- dplyr::inner_join(df_data, df_anat)

# add info about responsiveness
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive, z_snr))

# save
write.csv(df_data, 
          file.path(save_path, sprintf('%s_atlas-%s_acfTrial.csv', save_prefix, atlas_name)), 
          row.names=F)

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)

# rename atlas column name to "roi"
df_data <- rename(df_data, roi=custom)
```

<br>  

```{r}
mu <- filter(df_urear_acf, rhythm==!!rhythm) %>% pull(z_meterRel)

plt <- plot_feature(df_data, feature_name='z_meterRel', atlas='roi', task='listen', 
                    hline_spec=mu, hline_col='grey70', 
                    pntsize_ind=2, pntalpha_ind=0.5, pnt_col='lut', dodge_width=0.2,
                    pnt_col_mean='black', pntsize_mean=3, size_err=1.1, width_err=0,
                    y_lims=ylims_acf, show_labels=F, hline_zero=show_zero_line) 
plt

save_fig(file.path(save_path_fig, sprintf('%s_atlas-%s_urear-%s_zbeatACFtrial', 
                                          save_prefix, atlas_name, auditory_model_type)), 
         plt, width=1.9, height=2.5, png=F)
```

<br>  

```{r}
m <- lmer(z_meterRel ~ roi + (1|subject), data=df_data)
prep_anova_for_print(Anova(m, test='F'))
```

<br>  

```{r}
prep_bf_for_print(anovaBF(z_meterRel ~ roi + subject, data=df_data, whichRandom='subject', progress=F))
```

<br>  

```{r}
# posthoc 
pander(pairwise_contrasts_one_cond(m, var='roi', adjust_method='fdr', return_ci=TRUE)$res)
```

<br>  

```{r}
df_against_mu <- ddply(df_data, c('roi'), ttest_against_mu, mu=mu)
df_against_mu$pval <- p.adjust(df_against_mu$pval, method='fdr')
df_against_mu$signif <- signifStars(df_against_mu$pval)
pander(df_against_mu)
```

<br>  

```{r}
df_against_mu <- ddply(df_data, c('roi'), ttest_against_mu, mu=0)
df_against_0$pval <- p.adjust(df_against_0$pval, method='fdr')
df_against_0$signif <- signifStars(df_against_0$pval)
pander(df_against_0)
```




<br> 

# SMA


<br>   

Prepare contacts.  

```{r, fig.width=2, fig.height=3}
atlas_name <- 'sma'

# load anatomy
df_anat <- read.csv(file.path(feat_path, sprintf('prefix-%s_anatomy.csv', anat_prefix)))
df_anat <- fixFactors(df_anat)

# get only contacts in SMA and preSMA
df_anat <- filter(df_anat, custom %in% c('SMA', 'preSMA'))

# merge SMA and preSMA
df_anat$custom <- fct_recode(df_anat$custom, SMA='SMA', SMA='preSMA')

# subset responsive 
df_anat_resp <- dplyr::inner_join(df_anat, 
                                  df_zsnr_responsive %>% 
                                      filter(rhythm==!!rhythm & task==!!task) %>%
                                      select(subject, elec))
# count
df_count_all <- count_elec_roi(df_anat, 'custom')
df_count_resp <- count_elec_roi(df_anat_resp, 'custom')
pander(merge(df_count_all, df_count_resp, by='custom', suffixes=c('_total', '_responsive')) %>% rename(roi=custom))

```

```{r, fig.width=2, fig.height=3}
plt <- plot_count_roi_resp(df_count_all, df_count_resp, 'custom')

save_fig(file.path(save_path_fig, sprintf('%s_atlas-%s_responsive_counts', save_prefix, atlas_name)), 
         plt, width=2, height=3, png=F)

plt
```




<br>   

## FFT 

```{r}
# load FFT
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_fftAggrFreq.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task & rhythm==!!rhythm)

# subset in ROIs
df_data <- dplyr::inner_join(df_data, df_anat)

# add info about responsiveness
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive))

# save
write.csv(df_data, 
          file.path(save_path, sprintf('%s_atlas-%s_fft.csv', save_prefix, atlas_name)), 
          row.names=F)

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)

# rename atlas column name to "roi"
df_data <- rename(df_data, roi=custom)

```

<br>    

Plor the data.  

```{r, fig.width=2, fig.height=3}
plt <- plot_feature(df_data, feature_name='z_meterRel', atlas='roi', task='listen', hline_spec=mu, hline_col='grey70', 
                    pntsize_ind=2, pntalpha_ind=0.5, pnt_col='lut', dodge_width=0.2,
                    pnt_col_mean='black', pntsize_mean=3, size_err=1.1, width_err=0,
                    y_lims=ylims_fft, show_labels=F, hline_zero=show_zero_line) 

save_fig(file.path(save_path_fig, sprintf('%s_atlas-%s_urear-%s_zbeatFFT', 
                                          save_prefix, atlas_name, auditory_model_type)), 
         plt, width=1, height=2.5, png=F)

plt
```

<br>    

Compare beat-index against the brainstem model (one-sample t-test).  

```{r}
mu <- filter(df_urear_fft, rhythm==!!rhythm) %>% pull(z_meterRel)
t.test(df_data$z_meterRel, mu=mu)
```

<br>    

Compare beat-index against zero (one-sample t-test).  

```{r}
mu <- filter(df_urear_fft, rhythm==!!rhythm) %>% pull(z_meterRel)
t.test(df_data$z_meterRel, mu=0)
```



<br>   

## ACF 

```{r}
# load ACF
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_aggrACFtrial.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task & rhythm==!!rhythm)

# subset in ROIs
df_data <- dplyr::inner_join(df_data, df_anat)

# add info about responsiveness
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive, z_snr))

# save
write.csv(df_data, 
          file.path(save_path, sprintf('%s_atlas-%s_acfTrial.csv', save_prefix, atlas_name)), 
          row.names=F)

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)

# rename atlas column name to "roi"
df_data <- rename(df_data, roi=custom)

```


<br>    

Plot the data.  

```{r, fig.width=2, fig.height=3}
plt <- plot_feature(df_data, feature_name='z_meterRel', atlas='roi', task='listen', hline_spec=mu, hline_col='grey70', 
                    pntsize_ind=2, pntalpha_ind=0.5, pnt_col='lut', dodge_width=0.2,
                    pnt_col_mean='black', pntsize_mean=3, size_err=1.1, width_err=0,
                    y_lims=ylims_acf, show_labels=F, hline_zero=show_zero_line) 

save_fig(file.path(save_path_fig, sprintf('%s_atlas-%s_urear-%s_zbeatACFtrial', 
                                          save_prefix, atlas_name, auditory_model_type)), 
         plt, width=1, height=2.5, png=F)

plt
```

<br>    

Compare beat-index against the brainstem model (one-sample t-test).  

```{r}
mu <- filter(df_urear_acf, rhythm==!!rhythm) %>% pull(z_meterRel)
t.test(df_data$z_meterRel, mu=mu)
```

<br>    

Compare beat-index against zero (one-sample t-test).  

```{r}
mu <- filter(df_urear_acf, rhythm==!!rhythm) %>% pull(z_meterRel)
t.test(df_data$z_meterRel, mu=0)
```








<br> 

# Beat-index vs. SNR


<br>

Prepare contacts.  

```{r}
df_anat <- read.csv(file.path(feat_path, sprintf('prefix-%s_anatomy.csv', anat_prefix)))
df_anat <- fixFactors(df_anat)

# select ALL rois (auditory and associative, even if the given roi has small N responsive contacts)
df_anat <- dplyr::filter(df_anat, custom %in% all_rois)
```


<br> 

## FFT 

```{r}
# load FFT
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_fftAggrFreq.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task)

# subset in ROIs
df_data <- dplyr::inner_join(df_data, select(df_anat, subject, elec, custom, hem))

# add info about responsiveness
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive))

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)

# rename atlas column name to "roi"
df_data <- rename(df_data, roi=custom)

# log transform 
df_data$sum_magn_log <- log_trans(df_data$sum_magn)
df_data$z_snr_log <- log_trans(df_data$z_snr)

```

<br> 

Plot the data 

```{r, fig.height=3, fig.width=5}
ggplot(df_data, aes(z_snr_log, z_meterRel)) + 
    geom_hline(aes(yintercept=0), data=df_urear_fft, color='black') +  
    geom_hline(aes(yintercept=z_meterRel), data=df_urear_fft, color='gray80') +  
    geom_point(color='#288ec9', alpha=0.5) + 
    theme_cowplot() + 
    facet_wrap(~rhythm)
```

<br> 

Model beat-index vs z-snr for strongly-periodic rhythm.  

```{r}
# beat-index vs z-snr for strongly-periodic rhythm
m <- lmer(z_meterRel ~ z_snr_log + (1|subject), data=filter(df_data, rhythm=='sp'))
pander(summary(m)$coefficients)
```

```{r}
prep_bf_for_print(lmBF(z_meterRel ~ z_snr_log, whichRandom="subject", 
                       data=filter(df_data, rhythm=='sp'),
                       progress=F))
```

<br> 

Model beat-index vs z-snr for weakly-periodic rhythm.  

```{r}
# beat-index vs z-snr for weakly-periodic rhythm
m <- lmer(z_meterRel ~ z_snr_log + (1|subject), data=filter(df_data, rhythm=='wp'))
pander(summary(m)$coefficients)

```

```{r}
prep_bf_for_print(lmBF(z_meterRel ~ z_snr_log, whichRandom="subject", 
                       data=filter(df_data, rhythm=='wp'),
                       progress=F))
```


<br>   

## ACF 

```{r}
# load 
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_aggrACFtrial.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task)

# subset in ROIs
df_data <- dplyr::inner_join(df_data, select(df_anat, subject, elec, custom, hem))

# add info about responsiveness
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive, z_snr))

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)

# rename atlas column name to "roi"
df_data <- rename(df_data, roi=custom)

# log transform 
df_data$z_snr_log <- log_trans(df_data$z_snr)

```

<br> 

Plot the data 

```{r, fig.height=3, fig.width=5}
ggplot(df_data, aes(z_snr_log, z_meterRel)) + 
    geom_hline(aes(yintercept=0), data=df_urear_fft, color='black') +  
    geom_hline(aes(yintercept=z_meterRel), data=df_urear_acf, color='gray80') +  
    geom_point(color='#288ec9', alpha=0.5) + 
    theme_cowplot() + 
    facet_wrap(~rhythm)
```

<br> 

Model beat-index vs z-snr for strongly-periodic rhythm.  

```{r}
# beat-index vs z-snr for strongly-periodic rhythm
m <- lmer(z_meterRel ~ z_snr_log + (1|subject), data=filter(df_data, rhythm=='sp'))
pander(summary(m)$coefficients)
```

```{r}
prep_bf_for_print(lmBF(z_meterRel ~ z_snr_log, whichRandom="subject", 
                       data=filter(df_data, rhythm=='sp'),
                       progress=F))
```

<br> 

Model beat-index vs z-snr for weakly-periodic rhythm.  

```{r}
# beat-index vs z-snr for weakly-periodic rhythm
m <- lmer(z_meterRel ~ z_snr_log + (1|subject), data=filter(df_data, rhythm=='wp'))
pander(summary(m)$coefficients)
```

```{r}
prep_bf_for_print(lmBF(z_meterRel ~ z_snr_log, whichRandom="subject", 
                       data=filter(df_data, rhythm=='wp'),
                       progress=F))
```



<br> 

# Beat-index: ttest each ROI

Let's prepare tables with t-tests that can be pasted into the manuscript.  

```{r}
# function that exports to a nice table 
prepare_doc <- function(df){
    
    df$statistic <- round(df$statistic, 2)
    df$pval <- p_format(df$pval, digits=1)

    ft <- flextable(df)
    
    # Rename Columns
    ft <- set_header_labels(ft, 
                            custom = "ROI", 
                            statistic = "t", 
                            pval = "P", 
                            signif = '')
    # Make Header Bold
    ft <- flextable::bold(ft, part="header")
    
    # Align everything to the left
    ft <- flextable::align(ft, align = "left", part = "all")
    
    # Set Font to Calibri (all parts: header and body)
    ft <- flextable::font(ft, fontname = "Calibri", part = "all")
    ft <- fontsize(ft, size = 12, part = "all")
    
    # Adjust columns to content width
    ft <- autofit(ft)
    
    # Remove the fixed width property (this was making it unnecessarily wide)
    ft <- set_table_properties(ft, layout = "autofit", width=1)
    
    doc <- read_docx()
    doc <- body_add_flextable(doc, ft)
    return(doc) 
}

```


<br>    

Prepare contacts.  

```{r}
# load anatomy
df_anat <- read.csv(file.path(feat_path, sprintf('prefix-%s_anatomy.csv', anat_prefix)))
df_anat <- fixFactors(df_anat)

rois <- c(auditory_rois, assoc_rois)
if (response == 'LFP'){
    # remove SFG (too few contacts)
    rois <- rois[!rois %in% c('SFG')]
} else if (response == 'biLFP'){
    # don't forget to remove 'MFG' from here for biLFP (too few contacts)
    rois <- rois[!rois %in% c('SFG', 'MFG')]
}
             
df_anat <- dplyr::filter(df_anat, custom %in% rois)
df_anat$custom <- droplevels(df_anat$custom)
df_anat$custom <- factor(df_anat$custom, levels=rois)

# subset responsive 
df_anat_resp <- dplyr::inner_join(df_anat, 
                                  df_zsnr_responsive %>% 
                                      filter(rhythm==!!rhythm & task==!!task) %>%
                                      select(subject, elec))

```


<br>   

## FFT 

```{r}
# load FFT
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_fftAggrFreq.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task & rhythm==!!rhythm)

# subset in ROIs
df_data <- dplyr::inner_join(df_data, df_anat)

# add info about responsiveness
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive))

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)

# rename atlas column name to "roi"
df_data <- rename(df_data, roi=custom)

```

<br> 

Compare beat-index against the brainstem model (one-sample t-test).  

```{r}
mu <- filter(df_urear_fft, rhythm==!!rhythm) %>% pull(z_meterRel)

df_against_mu <- ddply(df_data, c('roi'), ttest_against_mu, mu=mu)
df_against_mu$pval <- p.adjust(df_against_mu$pval, method='fdr')
df_against_mu$signif <- signifStars(df_against_mu$pval)

doc <- prepare_doc(df_against_mu)
print(doc, target=file.path(save_path_fig, sprintf("%s_ttests_against_mu_fft.docx", save_prefix)))

```

<br> 

Compare beat-index against zero (one-sample t-test).  

```{r}
df_against_0 <- ddply(df_data, c('roi'), ttest_against_mu, mu=0)
df_against_0$pval <- p.adjust(df_against_0$pval, method='fdr')
df_against_0$signif <- signifStars(df_against_0$pval)

doc <- prepare_doc(df_against_0)
print(doc, target=file.path(save_path_fig, sprintf("%s_ttests_against_0_fft.docx", save_prefix)))

```



<br>    

## ACF 

```{r}
# load ACF
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_aggrACFtrial.csv', response)))
df_data <- fixFactors(df_data)

# subset rhythm and task
df_data <- filter(df_data, task==!!task & rhythm==!!rhythm)

# subset in ROIs
df_data <- dplyr::inner_join(df_data, df_anat)

# add info about responsiveness
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive, z_snr))

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)

# rename atlas column name to "roi"
df_data <- rename(df_data, roi=custom)

```

<br> 

Compare beat-index against the brainstem model (one-sample t-test).  

```{r}
mu <- filter(df_urear_acf, rhythm==!!rhythm) %>% pull(z_meterRel)

df_against_mu <- ddply(df_data, c('roi'), ttest_against_mu, mu=mu)
df_against_mu$pval <- p.adjust(df_against_mu$pval, method='fdr')
df_against_mu$signif <- signifStars(df_against_mu$pval)

doc <- prepare_doc(df_against_mu)
print(doc, target=file.path(save_path_fig, sprintf("%s_ttests_against_mu_acf.docx", save_prefix)))
```

<br> 

Compare beat-index against the brainstem model (one-sample t-test).  

```{r}
df_against_0 <- ddply(df_data, c('roi'), ttest_against_mu, mu=0)
df_against_0$pval <- p.adjust(df_against_0$pval, method='fdr')
df_against_0$signif <- signifStars(df_against_0$pval)

doc <- prepare_doc(df_against_0)
print(doc, target=file.path(save_path_fig, sprintf("%s_ttests_against_0_acf.docx", save_prefix)))
```



<br> 

# SNR: all ROIs  

<br>   

```{r}
# load anatomy
df_anat <- read.csv(file.path(feat_path, sprintf('prefix-%s_anatomy.csv', anat_prefix)))
df_anat <- fixFactors(df_anat)

rois <- c(auditory_rois, assoc_rois)
if (response == 'LFP'){
    # remove SFG (too few contacts)
    rois <- rois[!rois %in% c('SFG')]
} else if (response == 'biLFP'){
    # don't forget to remove 'MFG' from here for biLFP (too few contacts)
    rois <- rois[!rois %in% c('SFG', 'MFG')]
}
   
df_anat <- dplyr::filter(df_anat, custom %in% rois)
df_anat$custom <- droplevels(df_anat$custom)
df_anat$custom <- factor(df_anat$custom, levels=rois)

```


<br>  

Mean and SD of SNR per ROI.  

```{r}
# load FFT
df_data <- read.csv(file.path(feat_path, sprintf('response-%s_avg-time_fftAggrFreq.csv', response)))
df_data <- fixFactors(df_data)

# subset task
df_data <- filter(df_data, task==!!task)

# subset in ROIs
df_data <- dplyr::inner_join(df_data, df_anat)

# add info about responsiveness
df_data <- dplyr::inner_join(df_data, select(df_zsnr_all, subject, elec, rhythm, task, responsive))

# subset responsive 
df_data <- filter(df_data, responsive==TRUE)

df_summary <- summarySE(df_data, 'z_snr', c('rhythm', 'custom'))
df_summary$ci_low <- df_summary$z_snr - df_summary$ci
df_summary$ci_high <- df_summary$z_snr + df_summary$ci
df_summary <- select(df_summary, rhythm, custom, z_snr, ci_low, ci_high)

prepare_doc <- function(df){
    df$z_snr <- round(df$z_snr, 2)
    df$ci_low <- round(df$ci_low, 2)
    df$ci_high <- round(df$ci_high, 2)
    df$rhythm <- mapvalues(df$rhythm, 
                           from=c('sp', 'wp'), 
                           to=c('strongly-periodic', 'weakly-periodic'))    
    df$rhythm <- factor(df$rhythm, levels=c('weakly-periodic', 'strongly-periodic'))
    df <- dplyr::arrange(df, rhythm)
    ft <- flextable(df)
    ft <- set_table_properties(
        ft,
        width = 1,
        layout = "autofit"
    )
    doc <- read_docx()
    doc <- body_add_flextable(doc, ft)
}

doc <- prepare_doc(df_summary)

print(doc, target=file.path(save_path_fig,
                            sprintf("response-%s_task-%s_zsnr.docx", response, task)))

```


<br> 

# SNR: CAR vs. bipolar

```{r}

# NOTE: we won't select only responsive contacts to keep the comparison fair: indeed, the z-snr threshold was different
# for LFP and biLFP, which would bias the comparison. 

rois <- c("HG", "PT", "pSTG", "PP", "mSTG", "SMG", "SMC", "IFG", "MFG")

# -------------
# prepare  CAR 
# ------------

# load anatomy
df_anat <- read.csv(file.path(feat_path, sprintf('prefix-TDT_elecs_all_anatomy.csv')))
df_anat <- fixFactors(df_anat)

df_anat <- dplyr::filter(df_anat, custom %in% rois)
df_anat$custom <- droplevels(df_anat$custom)
df_anat$custom <- factor(df_anat$custom, levels=rois)

# load functional 
df_car <- read.csv(file.path(feat_path, sprintf('response-LFP_avg-time_fftAggrFreq.csv')))
df_car <- fixFactors(df_car)
df_car <- subset(df_car, rhythm=='wp' & task=='listen')
df_car <- select(df_car, c('subject', 'elec', 'rhythm', 'task', 'z_snr', 'sum_magn', 'z_meterRel'))
df_car$response <- 'LFP'

# subset ROIs only
df_car <- dplyr::inner_join(df_car, df_anat)

# -------------
# prepare bipolar 
# -------------

# load anatomy
df_anat <- read.csv(file.path(feat_path, sprintf('prefix-bipolar_elecs_all_anatomy.csv')))
df_anat <- fixFactors(df_anat)

df_anat <- dplyr::filter(df_anat, custom %in% rois)
df_anat$custom <- droplevels(df_anat$custom)
df_anat$custom <- factor(df_anat$custom, levels=rois)

df_bi <- read.csv(file.path(feat_path, sprintf('response-biLFP_avg-time_fftAggrFreq.csv')))
df_bi <- fixFactors(df_bi)
df_bi <- subset(df_bi, rhythm=='wp' & task=='listen')
df_bi <- select(df_bi, c('subject', 'elec', 'rhythm', 'task', 'z_snr', 'sum_magn', 'z_meterRel'))
df_bi$response <- 'biLFP'

# subset ROIs only
df_bi <- dplyr::inner_join(df_bi, df_anat)

# -------------
# concatenate
# -------------

df <- rbind(df_car, df_bi)
df$response <- factor(df$response, levels=c('LFP', 'biLFP'))

# log transform 
df$z_snr_log <- log_trans(df$z_snr)

```


```{r, fig.width=12, fig.height=4}

df_summary <- summarySE(df, measurevar='z_snr_log', groupvars=c('response', 'custom'))

cmap <- c(LFP='#aa62d1', biLFP='#cf9f11')

plt <- ggplot(df, aes(y=z_snr_log)) + 
    geom_half_violin(aes(split=response, fill=response),
                     color=NA, alpha=0.2,
                     position='identity', trim=FALSE) +
    geom_segment(data=df_summary,
               aes(x=0.05*(as.numeric(response)-1.5-0.3), 
                   xend=0.05*(as.numeric(response)-1.5+0.3), 
                   y=z_snr_log), 
               color='black', size=0.5) +
    geom_errorbar(data=df_summary,
                  aes(x=0.05*(as.numeric(response)-1.5), ymin=z_snr_log-ci, ymax=z_snr_log+ci), 
                  color='black', width=0, size=0.6) +
    scale_fill_manual(values=cmap) +
    theme_minimal() + 
    theme(
        axis.title.x = element_blank(),
        axis.text.x = element_blank()
    ) + 
    facet_wrap(~custom, nrow=1)

plt

save_fig(file.path(save_path_fig, sprintf('rhythm-wp_feat-logzsnr_LFP-vs-biLFP')), 
         plt, width=10, height=2, png=F)

```

```{r}
m <- lmer(z_snr_log ~ response + custom + (1|subject), data=df)
prep_anova_for_print(Anova(m, test='F'))
```

```{r}
prep_bf_for_print(anovaBF(z_snr_log ~ response + custom, data=df, whichRandom='subject', progress=F))
```


